\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors

### 2021-09-15 Manuscript/Manuscript.tex
Ddding presence absence model to ms

\documentclass[12pt,a4paper,]{article}
\usepackage[]{mathpazo}
\usepackage{setspace}
\setstretch{2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={ Trade-offs among plant floral and reproductive traits determine interactions with floral visitors},
            colorlinks=true,
            linkcolor=RoyalBlue,
            citecolor=Blue,
            urlcolor=RoyalBlue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and
reproductive traits determine interactions with floral visitors}
\author{}
\date{\vspace{-2.5em}}

@@

Here, we explore the potential trade-offs among plant floral and
reproductive traits and how these influence the structure of
plant-pollinator networks. First, we identify the major axes of floral
and reproductive trait variation and trade-offs that determine plant
form and function. Second, we investigate how plant species' position in
trait-space influences interaction strength with different guilds of
floral visitors. Finally, we investigate how the main axes of trait
variation and individual traits influence plant species roles within
networks using complementary interaction network metrics (i.e.,
interaction strength, normalized degree and specialization).

@@

\textbf{Plant strategies.} The phylogenetically informed principal
component analysis (pPCA) captured by the first two and three axes
51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
of 0.76. The first principal component (PC1) represented 26.72\% of the
trait variation and indicated a trade-off between flower number and
flower size. We refer to this axis as the `flower number - flower size
trade-off' as already described in previous
studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
Hence, one end of the spectrum comprised species with high investment in
flower number and plant height but small flower size, short style length
and low ovule number. The other end of this spectrum comprised species
that were short in height and invested in large flowers, long styles,
many ovules, but few flowers. The main contributing traits to PC1 were
plant height, flower number, ovule number and flower size (loadings
\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
style length also contributed moderately on PC1 (loading = -0.33). The
second principal component (PC2) represented 25.05\% of the trait
variation and indicated a trade-off between low and high pollinator
dependence. We refer to this axis as the `pollinator dependence
trade-off'. The main driver of trait variation on PC2 was autonomous
selfing (loading = 0.85) but the other traits (except ovule number) also
made moderate contributions (loadings from 0.27 to 0.4; Supplementary
Table S3). We found that high pollinator dependence was associated with
larger and a higher number of flowers, greater plant height and longer
styles. In contrast, species with high levels of autonomous selfing
tended to have fewer and smaller flowers, had shorter styles and were
shorter in height. Further, PC3 explained a considerable amount of trait
variability (19.17\%) and the main contributors to this axis were style
length (loading = -0.66) and the degree of autonomous selfing (loading =
-0.51). The remaining traits, apart from ovule number, were moderately
correlated to changes on PC3 (loadings from -0.23 to -0.46;
Supplementary Table S3). Thus, because style length was correlated with
all traits on PC3 and was the main driver of trait variation, we refer
to this axis as the `style length trade-off'. Further, the pPCA with the
subset of species that had nectar and pollen quantity data showed that
nectar quantity (microlitres of nectar per flower) was positively
associated with flower size, style length and ovule number (PC1,
23.40\%); and pollen quantity (pollen grains per flower) was positively
correlated with flower number and plant height and negatively associated
with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
explained similar variance with the first two principal components
(45.07\%) and similar associations of traits despite some variability in
the loadings (Supplementary Table S4).

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-1-1.pdf}
\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
life-history strategies.} Phylogenetically informed principal component
analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks
studies. The solid arrows indicate the direction of the different
quantitative traits (flower number, plant height, style length, flower
size, ovule number and level of autonomous selfing) across the two main
axes of trait variation. The length of the arrows indicate the weight of
the variables on each principal component and the labelled icons at
their end represent the extreme form of the trait continuum. The dashed
lines show the opposed direction of trait variation and the non-labelled
icons at their end illustrate the opposing extreme of the continuum.}
\end{figure}

We found that most categorical traits were statistically associated with
the first two axes of trait variation (Fig. 2 and Supplementary Table
S2). Flower symmetry, which was only associated with PC2 (Sum of squares
= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
In addition, we found with Tukey test statistical differences between
the different levels of categorical traits in the trait space
(Supplementary Fig. S7). Regarding self compatibility, we found larger
differences on PC2 (i.e., species with unisexual flowers that were self
incompatibile were statistically differentiated from species with
partial or full self compatibility; Supplementary Fig. S7a and Fig.
S7b). Life forms differed statistically across both axes of trait
variation and followed a gradient of larger life forms (trees and
shrubs) with higher pollinator dependence to smaller ones (herbs) with
lower pollinator dependence (Supplementary Fig. S7c and Fig. S7d).
Consequently, lifespan also followed this gradient but perennial and
short lived species only differed statistically on PC2 (Supplementary
Fig. S7e and Fig. S7f). Species with unisexual flowers (monoecious and
dioecious) were clustered on both extremes of the first two principal
components and had the highest pollinator dependence and highest number
of flowers (Supplementary Fig. S7g and Fig. S7h). Moreover, we found
that the campanulate and capitulum flower shapes were differentiated
from tube, papilionaceous, open and brush shapes in the trait space. The
former morphologies had larger flowers and greater pollinator
dependence, while the latter had higher flower number and greater
autonomous selfing (Supplementary Fig. S7i and Fig. S7j). Regarding
flower symmetry, zygomorphic flowers were associated with lower levels
of pollinator dependence, whereas actinomorphic flowers had higher
levels of pollinator dependence (Supplementary Fig. S7k and Fig. S7l).

@@

\textbf{Visitation patterns.} The main axes of trait variation explained
little of the overall visitation rates (\(conditional R2 = 0.31\);
\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
interaction with the different floral visitors guilds (Fig. 3). All
floral visitors guilds visited plant species with higher pollinator
dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
Non-Anthophila-Hymenoptera showed greater visitation rates on plant
species with larger styles and higher levels of selfing; while
Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
3f). Furthermore, when running an additional model that separates the
most represented families of Anthophila-Hymenoptera (bees;
\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
family Apidae was the main driver of the observed patterns
(Supplementary Fig. S8).

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Visitation
rates across the three main axes of trait variation.} Fitted posterior
estimates of the number of visits made by the different floral visitors
guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest
of guilds (d, e and f) were plotted separately for visualization
purposes. In addition, we trimmed the plotting area that was over the
95th percentile to improve visualisation. PC1 represents the flower
number - flower size trade-off, PC2 represents the pollinator dependence
trade-off and PC3, the style length trade-off.}
\end{figure}

@@

\textbf{Plant species functional roles.} The variance of the different
plant species level metrics was poorly explained by the three main axes
of trait variation (Supplementary Fig. S9; interaction frequency
\textasciitilde{} PCs, \(conditional R2 = 0.11\),
\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
\textasciitilde{} PCs, \(conditional R2 = 0.37\),
\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
PC1 and PC3 for interaction frequency and specialization. On the flower
number - flower size trade-off (PC1), interaction frequency was higher
for plant species with more flowers but was lower for plant species with
larger flowers. On PC1, specialization showed the opposite trend. On the
style length trade-off (PC3), interaction frequency was lower for plants
with shorter styles and lower autonomous selfing and higher for species
with longer styles and higher autonomous selfing. Again, specialization
showed the opposite trend to interaction frequency.

@@

To conclude, we provide the first description of plant floral and
reproductive trade-offs using a large global dataset of plant traits and
interactions with floral visitors. This allowed us to identify the major
reproductive strategies of flowering plants and how plant life
strategies determine their interaction with floral visitor guilds.
Although the percentage of explained variation found with the first two
axes (\textasciitilde{}50\%) is lower than other studies that have
evaluated life histories with vegetative
traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
this percentage is consistent with the largest and most recent study
that have characterized life strategies with both vegetative and
reproductive (i.e., semelparity and iteroparity)
traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. Future
work needs to integrate these floral and reproductive compromises with
the already described vegetative and physiological
trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
create a more comprehensive spectra of trait
variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
Further, the varying level of phylogenetic signal among traits deserves
further attention to understand evolutionary changes on mating and
flower morphology in response to
pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}}.
Finally, a more complete description of the macroecological patterns of
plant-pollinator interactions including unrepresented areas of the
world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits
that have been largely ignored (e.g., floral rewards and plant mating
system) are needed to progress in our understanding of the global
patterns in plant-pollinator interactions.

@@

\textbf{Networks analyses.} Analyses were conducted on the subset of 60
weighted networks with interaction frequency sampled in a unique
flowering season and site, which included 556 plant and 1,126 pollinator
species. In total, our weighted network dataset (excluding meta-webs)
included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with
plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions
and 362 non-Anthophila-Hymenoptera interactions. Although floral
visitors are not always pollinators and the frequency of visits does not
consider each pollinator species
efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
visitation rate provides valuable information of the contribution of
floral visitors to
pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
Sampling methods varied across networks but this was accounted for in
analyses by considering them in the random effects of the modelling
process. All analyses were conducted in R version \emph{4.0.3}.

\textbf{Visitation patterns.} We used Bayesian modelling (see below for
details) to explore the effect of floral visitors groups and the main
axes of trait variation (pPCA with imputed dataset) on floral visits per
plant species. For this, we divided floral visitors into six main guilds
that differ in life form, behaviour and are likely to play a similar
ecological role: (i) Hymenoptera-Anthophila (bees), (ii)
Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
Coleoptera. Moreover, because Hymenoptera-Anthophila was the most
represented group with 2,256 records and had the highest frequency of
visits of all groups, we also explored the visitation rate of the main
Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae,
Halictidae and Megachilidae) on the trait space. In addition, we found
that \emph{Apis mellifera} was the floral visitor with the largest
proportion of records counted (7.55\% of the total). This finding is
consistent with previous research showing that \emph{A. mellifera} was
the most frequent floral visitor in a similar dataset of 80
plant-pollinator networks in natural
ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,
to control for the effect of \emph{A. mellifera} on the observed
visitation patterns of bees, we conducted an analogous analysis
excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was
partly driving some of the observed trends on PC1 (Supplementary Fig.
S3). However, we did not detect major differences on PC2 and PC3.

>>>>

\documentclass[12pt,a4paper,]{article}
\usepackage[]{mathpazo}
\usepackage{setspace}
\setstretch{2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={ Trade-offs among plant reproductive traits determine interactions with floral visitors},
            colorlinks=true,
            linkcolor=RoyalBlue,
            citecolor=Blue,
            urlcolor=RoyalBlue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\title{\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant
reproductive traits determine interactions with floral visitors}
\author{}
\date{\vspace{-2.5em}}

@@

Here, we explore the potential trade-offs among plant floral and
reproductive traits and how these influence the structure of
plant-pollinator networks. First, we identify the major axes of floral
and reproductive trait variation and trade-offs that determine plant
form and function. Second, we investigate how plant species' position in
trait-space influences their interaction strength with different guilds
of floral visitors. Finally, we investigate how the main axes of trait
variation and individual traits influence plant species roles within
networks.

@@

\textbf{Plant strategies.} The phylogenetically informed principal
component analysis (pPCA) captured by the first two and three axes
51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
of 0.76. The first principal component (PC1) represented 26.72\% of the
trait variation and indicated a trade-off between flower number and
flower size. We refer to this axis as the `flower number - flower size
trade-off', as already described in previous
studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
Hence, one end of the spectrum comprised species with high investment in
flower number and plant height but small flower size, short style length
and low ovule number. The other end of this spectrum comprised species
that were short in height and invested in large flowers, long styles,
many ovules, but few flowers. The main contributing traits to PC1 were
plant height, flower number, ovule number and flower size (loadings
\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
style length also contributed moderately on PC1 (loading = -0.33). The
second principal component (PC2) represented 25.05\% of the trait
variation and indicated a trade-off between low and high pollinator
dependence. We refer to this axis as the `pollinator dependence
trade-off'. The main driver of trait variation on PC2 was autonomous
selfing (loading = 0.85) but the other traits (except ovule number) also
made moderate contributions (loadings from 0.27 to 0.4; Supplementary
Table S3). We found that high pollinator dependence was associated with
larger and a higher number of flowers, greater plant height and longer
styles. In contrast, species with high levels of autonomous selfing
tended to have fewer and smaller flowers, had shorter styles and were
shorter in height. Further, PC3 explained a considerable amount of trait
variability (19.17\%) and the main contributors to this axis were style
length (loading = -0.66) and the degree of autonomous selfing (loading =
-0.51). The remaining traits, apart from ovule number, were moderately
correlated to changes on PC3 (loadings from -0.23 to -0.46;
Supplementary Table S3). Thus, because style length was correlated with
all traits on PC3 and was the main driver of trait variation, we refer
to this axis as the `style length trade-off'. Further, the pPCA with the
subset of species that had nectar and pollen quantity data showed that
nectar quantity (microlitres of nectar per flower) was positively
associated with flower size, style length and ovule number (PC1,
23.40\%); and pollen quantity (pollen grains per flower) was positively
correlated with flower number and plant height and negatively associated
with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
explained similar variance with the first two principal components
(45.07\%) and similar associations of traits despite some variability in
the loadings (Supplementary Table S4).

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-1-1.pdf}
\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
life-history strategies.} Phylogenetically informed principal component
analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network
studies. The solid arrows indicate the direction of the different
quantitative traits (flower number, plant height, style length, flower
size, ovule number and level of autonomous selfing) across the two main
axes of trait variation. The length of the arrows indicate the weight of
the variables on each principal component and the dashed lines show the
opposed direction of trait variation. The icons at both ends of arrows
and dashed lines illustrate the extreme form of the trait continuum.}
\end{figure}

We found that most categorical traits were statistically associated with
the first two axes of trait variation (Fig. 2 and Supplementary Table
S2). Flower symmetry, which was only associated with PC2 (Sum of squares
= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
In addition, we found (with a Tukey test) statistical differences
between the different levels of categorical traits in the trait space
(Supplementary Fig. S7). Regarding self compatibility, we found larger
differences on PC2 (i.e., species with unisexual flowers that were self
incompatible were statistically differentiated from species with partial
or full self compatibility; Supplementary Fig. S7a and Fig. S7b). Life
forms differed statistically across both axes of trait variation and
followed a gradient of larger life forms (trees and shrubs) with higher
pollinator dependence to smaller ones (herbs) with lower pollinator
dependence (Supplementary Fig. S7c and Fig. S7d). Consequently, lifespan
also followed this gradient but perennial and short lived species only
differed statistically on PC2 (Supplementary Fig. S7e and Fig. S7f).
Species with unisexual flowers (monoecious and dioecious) were clustered
on both extremes of the first two principal components and had the
highest pollinator dependence and highest number of flowers
(Supplementary Fig. S7g and Fig. S7h). Moreover, we found that the
campanulate and capitulum flower shapes were differentiated from tube,
papilionaceous, open and brush shapes in the trait space. The former
morphologies had larger flowers and greater pollinator dependence, while
the latter had higher flower number and greater autonomous selfing
(Supplementary Fig. S7i and Fig. S7j). Regarding flower symmetry,
zygomorphic flowers were associated with lower levels of pollinator
dependence, whereas actinomorphic flowers had higher levels of
pollinator dependence (Supplementary Fig. S7k and Fig. S7l).

@@

\textbf{Visitation patterns.} The main axes of trait variation explained
little of the overall visitation rates (\(conditional R2 = 0.31\);
\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
interaction with the different floral visitor guilds (Fig. 3). All
floral visitor guilds visited plant species with higher pollinator
dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
Non-Anthophila-Hymenoptera showed greater visitation rates on plant
species with larger styles and higher levels of selfing; while
Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
3f). Furthermore, when running an additional model that separates the
most represented families of Anthophila-Hymenoptera (bees;
\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
family Apidae was the main driver of the observed patterns
(Supplementary Fig. S8).

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Interaction
(yes/no) and visitation rates across the three main axes of trait
variation per floral visitor guild.} Fitted posterior estimates of the
presence/absence of interaction (a, b and c) and number of visits (d, e
and f) made by the different floral visitors guilds in relation to PC1,
PC2 and PC3. PC1 represents the flower number - flower size trade-off,
PC2 represents the pollinator dependence trade-off and PC3, the style
length trade-off.}
\end{figure}

@@

\textbf{Plant species functional roles.} The variance of the different
plant species-level network metrics was poorly explained by the three
main axes of trait variation (Supplementary Fig. S9; interaction
frequency \textasciitilde{} PCs, \(conditional R2 = 0.11\),
\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
\textasciitilde{} PCs, \(conditional R2 = 0.37\),
\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
PC1 and PC3 for interaction frequency and specialization. On the flower
number - flower size trade-off (PC1), interaction frequency was higher
for plant species with more flowers but was lower for plant species with
larger flowers. On PC1, specialization showed the opposite trend. On the
style length trade-off (PC3), interaction frequency was lower for plants
with shorter styles and lower autonomous selfing and higher for species
with longer styles and higher autonomous selfing. Again, specialization
showed the opposite trend to interaction frequency.

@@

To conclude, we provide the first description of plant floral and
reproductive trade-offs using a large global dataset of plant traits and
interactions with floral visitors. This allowed us to identify the major
reproductive strategies of flowering plants and how plant life
strategies determine their interaction with floral visitor guilds.
Although the percentage of explained variation found with the first two
axes (\textasciitilde{}50\%) is lower than other studies that have
evaluated life histories with vegetative
traits\textsuperscript{\protect\hyperlink{ref-diaz2016}{18},\protect\hyperlink{ref-carmona2021}{19}},
this percentage is consistent with the largest and most recent study
that has characterized life strategies with both vegetative and
reproductive (i.e., semelparity and iteroparity)
traits\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}}. Future
work needs to integrate these floral and reproductive compromises with
the already described vegetative and physiological
trade-offs\textsuperscript{\protect\hyperlink{ref-diaz2016}{18}} to
create a more comprehensive spectrum of trait
variation\textsuperscript{\protect\hyperlink{ref-roddy2021}{10}}.
Further, the varying level of phylogenetic signal among traits deserves
further attention to understand evolutionary changes on mating and
flower morphology in response to
pollinators\textsuperscript{\protect\hyperlink{ref-gervasi2017}{42},\protect\hyperlink{ref-mackin2021}{43}}.
Finally, a more complete description of the macroecological patterns of
plant-pollinator interactions including unrepresented areas of the
world\textsuperscript{\protect\hyperlink{ref-poisot2021}{44}} and traits
that have been largely ignored (e.g., floral rewards and plant mating
system) are needed to progress in our understanding of the global
patterns in plant-pollinator interactions.

@@

\textbf{Network analyses.} Analyses were conducted on the subset of 60
weighted networks with interaction frequency sampled in a unique
flowering season and site, which included 556 plant and 1,126 pollinator
species. In total, our weighted network dataset (excluding meta-webs)
included 2,256 interactions of Anthophila-Hymenoptera (i.e., bees) with
plants, 1,768 non-Syrphidae-Diptera interactions, 845 Syrphidae
interactions, 437 Lepidoptera interactions, 432 Coleoptera interactions
and 362 non-Anthophila-Hymenoptera interactions. Although floral
visitors are not always pollinators and the frequency of visits does not
consider each pollinator species
efficiency\textsuperscript{\protect\hyperlink{ref-ballantyne2015}{57}},
visitation rate provides valuable information of the contribution of
floral visitors to
pollination\textsuperscript{\protect\hyperlink{ref-vazquez2005}{58},\protect\hyperlink{ref-vazquez2012}{59}}.
Sampling methods varied across networks but this was accounted for in
analyses by considering them in the random effects of the modelling
process. All analyses were conducted in R version \emph{4.0.3}.

\textbf{Visitation patterns.} We used Bayesian modelling (see below for
details) to explore the effect of floral visitor groups and the main
axes of trait variation (pPCA with imputed dataset) on floral visits per
plant species. For this, we divided floral visitors into six main guilds
that differ in life form, behaviour and are likely to play a similar
ecological role: (i) Hymenoptera-Anthophila (bees), (ii)
Hymenoptera-non-Anthophila (non-bee Hymenoptera), (iii)
Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi)
Coleoptera. Moreover, because Hymenoptera-Anthophila was the most
represented group with 2,256 records and had the highest frequency of
visits of all groups, we also explored the visitation rate of the main
Hymenoptera-Anthophila families (Andrenidae, Apidae, Colletidae,
Halictidae and Megachilidae) on the trait space. In addition, we found
that \emph{Apis mellifera} was the floral visitor with the largest
proportion of records counted (7.55\% of the total). This finding is
consistent with previous research showing that \emph{A. mellifera} was
the most frequent floral visitor in a similar dataset of 80
plant-pollinator networks in natural
ecosystems\textsuperscript{\protect\hyperlink{ref-hung2018}{60}}. Hence,
to control for the effect of \emph{A. mellifera} on the observed
visitation patterns of bees, we conducted an analogous analysis
excluding \emph{A. mellifera}. We found that \emph{A. mellifera}, was
partly driving some of the observed trends on PC1 (Supplementary Fig.
S3). However, we did not detect major differences on PC2 and PC3.
